---
title: "Workforce Statistics"
author: "WED"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

# Workforce Statistics

```{r packages, echo=FALSE, include=FALSE}
pkgs = c( "tailwindr", "ggplot2", 
         "ggthemes", "scales")
sapply(pkgs, require, character.only = TRUE)
```

```{r load-data, echo=FALSE}
# Import data needed by your reports.
```

### Key Takeaways
You can write a brief summary of your analysis for management or other analysts.
- You can use unordered lists like this one.
- Add emphasis using **bold** or *italics*.  
- Insert dynamic data with R code directly in-line, like today's date is `r Sys.Date()`.

#### A Picture is Worth 1,000 Rows of Data
Display visualizations using the `ggplot2` package or other graphics packages.   
```{r fte-count-historical, echo=FALSE, fig.width=9}
mtcars <- mutate(mtcars,cyl=factor(cyl,ordered=TRUE,levels=c(4,6,8)))
head(mtcars,n=6)

ggplot(mtcars,aes(x=mpg)) + 
  geom_histogram(binwidth=5) +
  labs(title = "Cars Data", x = "Miles Per Gallon", y = "Number of Cars") +
  theme_hc()

```


Using Rmarkdown, you can write neat formulas like the vacancy rate formula 
$$
\frac{ (Authorized FTE - Filled Incumbents) } { (Authorized FTE - Filled Incumbents)+Incumbents } * 100 
$$

Output this report as an HTML document or change the output to a Word doc.
