---
output: 
  html_document: 
    highlight: zenburn 
    self_contained: false 
    slim_css: TRUE 
    css: []
    theme: null
---

<!-- Include CDN JavaScript -->
<script src='https://cdn-tailwindcss.vercel.app/?plugins=forms,typography,aspect-ratio,line-clamp'></script>

<div class="prose mx-20 my-20 max-w-none">


<h1 class="text-center mb-4">Workforce Statistics</h1>

<div class="flex justify-center space-x-8 mb-12">
<span class="text-base leading-6 font-medium text-gray-800">By <span class="text-semibold">WED</span></span> 
<span>·</span>
<span class="text-base leading-6 font-medium text-gray-800"><time>`r format(Sys.time(), '%B %d, %Y')`</time></span>
</div>

```{r, results = "asis", echo = F}
shiny.tailwind::use_tailwind()
```

```{r packages, echo=FALSE, include=FALSE}
pkgs = c( "tailwindr", "ggplot2", "data.table", 
          "ggthemes", "scales", "DT")
sapply(pkgs, require, character.only = TRUE)
```

```{r load-data, echo=FALSE}
# Import data needed by your reports.
```

### Key Takeaways
You can write a brief summary of your analysis for management or other analysts.
- You can use unordered lists like this one.
- Add emphasis using **bold** or *italics*.  
- Insert dynamic data with R code directly in-line, like today's date is `r Sys.Date()`.

#### A Picture is Worth 1,000 Rows of Data
Display visualizations using the `ggplot2` package or other graphics packages.   
```{r fte-count-historical, echo=FALSE, fig.width=9}
mtcars <- mutate(mtcars,cyl=factor(cyl,ordered=TRUE,levels=c(4,6,8)))
head(mtcars,n=6)

ggplot(mtcars,aes(x=mpg)) + 
  geom_histogram(binwidth=5) +
  labs(title = "Cars Data", x = "Miles Per Gallon", y = "Number of Cars") +
  theme_hc()

```


Using Rmarkdown, you can write neat formulas like the vacancy rate formula 
$$
\frac{ (Authorized FTE - Filled Incumbents) } { (Authorized FTE - Filled Incumbents)+Incumbents } * 100 
$$


<div class="flex flex-row gap-x-20">
<div class="flex flex-col"> 
#### Example Table 1
Display two interactive tables side-by-side.
```{r cw-tbl, echo=FALSE, fig.width=5}

mtcars = data.table(mtcars)

DT::datatable( 
  mtcars, 
  rownames = FALSE,
  filter = 'top',
  extensions = 'Buttons',
  caption = "This table can be downloaded and printed",
  options = list(
    dom = 'Blrtip',
    buttons = c('excel', 'pdf', 'print'),
    pageLength = 20,
    lengthMenu = c(5, 10, 15, 20)
  )
)

```
</div>

<div class="flex flex-col">
#### Example Table 2
Display two interactive tables side-by-side.
```{r dept_tbls, echo=FALSE, fig.width=4}

iris = data.table(iris)

DT::datatable( 
  iris, rownames = FALSE,
  filter = 'top',
  extensions = 'Buttons',
  caption = "This is the famous iris dataset",
  options = list(
    dom = 'Blrtip',
    buttons = c('excel', 'pdf', 'print'),
    pageLength = 20,
    lengthMenu = c(5, 10, 15, 20, 50, 100)
  )
)
```
</div>
</div>
